GOmeth test

### 2023-11-21 figs/GSE158422_rna_int.Rmd
Prefer UCSC annotations

anno <- getAnnotation(IlluminaHumanMethylationEPICanno.ilm10b4.hg19)
myann <- data.frame(anno[,c("UCSC_RefGene_Name","Regulatory_Feature_Group","Islands_Name","Relation_to_Island")])
gp <- myann[,"UCSC_RefGene_Name",drop=FALSE]
gp2 <- strsplit(gp$UCSC_RefGene_Name,";")
names(gp2) <- rownames(gp)
sets <- split(rep(names(gp2), lengths(gp2)), unlist(gp2))
summary(unlist(lapply(sets,length)))

@@

table(dm$Regulatory_Feature_Group)

@@

# promoter
dmpr <- dm[grep("Promoter",dm$Regulatory_Feature_Group),]
dmpragg <- agg(dm=dmpr,cores=16)
str(dmpragg)
head(dmpragg$gme_res_df)
dim(dmpr)
dim(dmpragg$gme_res_df)
mmpr <- dmpragg$gme_res_df[,"mean",drop=FALSE]
mmprres <- mitch_calc(mmpr, genesets=gs_symbols, priority="effect",cores=32)
mmprres_up <- subset(mmprres$enrichment_result,s.dist>0 & p.adjustANOVA < 0.05)
mmprres_dn <- subset(mmprres$enrichment_result,s.dist<0 & p.adjustANOVA < 0.05)
nrow(mmprres_up)
nrow(mmprres_dn)
head(mmprres_up,20)
head(mmprres_dn,20)

# ex-promoter
dmx <- dm[grep("Promoter",dm$Regulatory_Feature_Group,invert=TRUE),]
dmxagg <- agg(dm=dmx,cores=16)
str(dmxagg)
head(dmxagg$gme_res_df)
dim(dmx)
dim(dmxagg$gme_res_df)
mmx <- dmxagg$gme_res_df[,"mean",drop=FALSE]
mmxres <- mitch_calc(mmx, genesets=gs_symbols, priority="effect",cores=32)
mmxres_up <- subset(mmxres$enrichment_result,s.dist>0 & p.adjustANOVA < 0.05)
mmxres_dn <- subset(mmxres$enrichment_result,s.dist<0 & p.adjustANOVA < 0.05)
nrow(mmxres_up)
nrow(mmxres_dn)
head(mmxres_up,20)
head(mmxres_dn,20)

>>>>

anno <- getAnnotation(IlluminaHumanMethylationEPICanno.ilm10b4.hg19)
myann <- data.frame(anno[,c("UCSC_RefGene_Name","GencodeCompV12_Group","Islands_Name","Relation_to_Island")])
gp <- myann[,"UCSC_RefGene_Name",drop=FALSE]
gp2 <- strsplit(gp$UCSC_RefGene_Name,";")
names(gp2) <- rownames(gp)
sets <- split(rep(names(gp2), lengths(gp2)), unlist(gp2))
summary(unlist(lapply(sets,length)))

@@

table(dm$UCSC_RefGene_Group)

@@

# promoter
dmpr <- dm[grep("Promoter",dm$UCSC_RefGene_Group),]
dmpragg <- agg(dm=dmpr,cores=16)
str(dmpragg)
head(dmpragg$gme_res_df)
dim(dmpr)
dim(dmpragg$gme_res_df)
mmpr <- dmpragg$gme_res_df[,"mean",drop=FALSE]
mmprres <- mitch_calc(mmpr, genesets=gs_symbols, priority="effect",cores=32)
mmprres_up <- subset(mmprres$enrichment_result,s.dist>0 & p.adjustANOVA < 0.05)
mmprres_dn <- subset(mmprres$enrichment_result,s.dist<0 & p.adjustANOVA < 0.05)
nrow(mmprres_up)
nrow(mmprres_dn)
head(mmprres_up,20)
head(mmprres_dn,20)

# ex-promoter
dmx <- dm[grep("Promoter",dm$UCSC_RefGene_Group,invert=TRUE),]
dmxagg <- agg(dm=dmx,cores=16)
str(dmxagg)
head(dmxagg$gme_res_df)
dim(dmx)
dim(dmxagg$gme_res_df)
mmx <- dmxagg$gme_res_df[,"mean",drop=FALSE]
mmxres <- mitch_calc(mmx, genesets=gs_symbols, priority="effect",cores=32)
mmxres_up <- subset(mmxres$enrichment_result,s.dist>0 & p.adjustANOVA < 0.05)
mmxres_dn <- subset(mmxres$enrichment_result,s.dist<0 & p.adjustANOVA < 0.05)
nrow(mmxres_up)
nrow(mmxres_dn)
head(mmxres_up,20)
head(mmxres_dn,20)

### 2023-11-21 figs/GSE158422_sensitivity.Rmd
Prefer UCSC annotations

anno <- getAnnotation(IlluminaHumanMethylationEPICanno.ilm10b4.hg19)
myann <- data.frame(anno[,c("UCSC_RefGene_Name","Regulatory_Feature_Group","Islands_Name","Relation_to_Island")])

>>>>

anno <- getAnnotation(IlluminaHumanMethylationEPICanno.ilm10b4.hg19)
myann <- data.frame(anno[,c("UCSC_RefGene_Name","UCSC_RefGene_Group","Islands_Name","Relation_to_Island")])

### 2023-11-21 figs/gmea.Rmd
Prefer UCSC annotations

ann450k <- getAnnotation(IlluminaHumanMethylation450kanno.ilmn12.hg19)
myann <- data.frame(ann450k[,c("UCSC_RefGene_Name","Regulatory_Feature_Group")])
gp <- myann[,"UCSC_RefGene_Name",drop=FALSE]
gp2 <- strsplit(gp$UCSC_RefGene_Name,";")
names(gp2) <- rownames(gp)
sets <- split(rep(names(gp2), lengths(gp2)), unlist(gp2))
promoters <- grep("Prom",myann$Regulatory_Feature_Group)

>>>>

ann450k <- getAnnotation(IlluminaHumanMethylation450kanno.ilmn12.hg19)
myann <- data.frame(ann450k[,c("UCSC_RefGene_Name","UCSC_RefGene_Group")])
gp <- myann[,"UCSC_RefGene_Name",drop=FALSE]
gp2 <- strsplit(gp$UCSC_RefGene_Name,";")
names(gp2) <- rownames(gp)
sets <- split(rep(names(gp2), lengths(gp2)), unlist(gp2))
promoters <- grep("Prom",myann$UCSC_RefGene_Group)

### 2023-11-21 figs/step_01a_GSE74548_prep.Rmd
Prefer UCSC annotations

suppressPackageStartupMessages({
  library("missMethyl")
  library("GEOquery")
  library("limma")
  library("topconfects")
  library("minfi")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylation450kanno.ilmn12.hg19")
  library("DMRcate")
  library("mitch")
  library("kableExtra")
  library("forestplot")
  library("RColorBrewer")
  library("plyr")
  library("R.utils")
  library("eulerr")
  library("gplots")
  library("reshape2")
  library("beeswarm")
  library("RCircos")
})
# Annotation
ann450k <- getAnnotation(IlluminaHumanMethylation450kanno.ilmn12.hg19)
myann <- data.frame(ann450k[,c("UCSC_RefGene_Name","Regulatory_Feature_Group")])
promoters <- grep("Prom",myann$Regulatory_Feature_Group)

>>>>

suppressPackageStartupMessages({
  library("missMethyl")
  library("GEOquery")
  library("limma")
  library("topconfects")
  library("minfi")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylation450kanno.ilmn12.hg19")
  library("DMRcate")
  library("mitch")
  library("kableExtra")
  library("forestplot")
  library("RColorBrewer")
  library("plyr")
  library("R.utils")
  library("eulerr")
  library("gplots")
  library("reshape2")
  library("beeswarm")
  library("RCircos")
})
# Annotation
ann450k <- getAnnotation(IlluminaHumanMethylation450kanno.ilmn12.hg19)
myann <- data.frame(ann450k[,c("UCSC_RefGene_Name","UCSC_RefGene_Group")])
promoters <- grep("Prom",myann$UCSC_RefGene_Group)

### 2023-11-21 figs/step_01b_test_gometh.Rmd
Prefer UCSC annotations

ann450k <- getAnnotation(IlluminaHumanMethylation450kanno.ilmn12.hg19)
myann <- data.frame(ann450k[,c("UCSC_RefGene_Name","Regulatory_Feature_Group")])
promoters <- grep("Prom",myann$Regulatory_Feature_Group)

>>>>

ann450k <- getAnnotation(IlluminaHumanMethylation450kanno.ilmn12.hg19)
myann <- data.frame(ann450k[,c("UCSC_RefGene_Name","UCSC_RefGene_Group")])
promoters <- grep("Prom",myann$UCSC_RefGene_Group)
